
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\LARGE\textcolor{white}{\textbf{\MakeUppercase{David Guillermo}}}}} % First name
	%\colorbox{black}{{\LARGE\textcolor{white}{\textbf{\MakeUppercase{Guillermo }}}}} % First name

	\colorbox{black}{{\LARGE\textcolor{white}{\textbf{\MakeUppercase{López Vázquez}}}}} % Last name
	%\colorbox{black}{{\LARGE\textcolor{white}{\textbf{\MakeUppercase{Vázquez }}}}} % Last name

	\vspace{6pt}
	
	{\huge Mobile Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.375\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Eje Central Lázaro Cardenas 195 CDMX}\\
	\icon{Phone}{12}{222 780 2098}\\
	\icon{At}{12}{\href{mailto:ginppian@icloud.com}{ginppian@icloud.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://www.ginppian.com}{ginppian.com}}\\
	\icon{Github}{12}{\href{https://github.com/ginppian}{github.com/ginppian}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/@ginppian}{@ginppian}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	%\lorem \lorem \lorem \lorem \lorem\\ % Dummy text
	I consider myself passionate about ubiquitous technology, especially the development of mobile applications.
I like the native development (in both main platforms, iOS and Android), I consider that it feeds all the sensors that the device brings and enriches each application.
I like the use of good programming practices, such as design patterns and clean architecture. Before making an implementation, I consider that the tests are very important. And for the optimization of the application, the efficiency of the algorithms is very important too.
I am currently interested in the implementation of Artificial Intelligence and Deep Learning in mobile applications.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Java}{60}
		\baritem{Android}{60}
		\baritem{Objective-C}{80}
		\baritem{Swift}{100}
		\baritem{HTML5}{70}
		\baritem{PHP}{75}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{3.8/AndroidStudio, 4.5/Xcode, 3.3/Workbench, 4/Git, 3.5/XAMPP}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{08/2016 -- 12/2016\\\footnotesize{Freelance}}
		{iOS Developer}
		{Individual: David Santiago Fernandez Bermejo Morales. In Workana.com}
		{Tourist center "Lagunas De Ruidera" Spain.
		\\ \texttt{CoreLocation}\slashsep\texttt{Local and Remote Notifications}\slashsep\texttt{Git and Bitbucket}		
		}
	\entry
		{01/2017 -- 03/2017}
		{iOS Developer}
		{CUVITEK}
		{UFind App, iTunes ID: 1220932121.
		\\ \texttt{REST APIs and network requests}\slashsep\texttt{Facebook SDK}\slashsep\texttt{Firebase Cloud Messaging}		
		}
		\entry
		{04/2017 -- 10/2017}
		{Android Developer}
		{Financial "Para Crecer".}
		{Internal App
		\\ \texttt{REST APIs and native network requests}\slashsep\texttt{Location and Google Maps}\slashsep\texttt{Responsive layouts}		
		}
		\entry
		{11/2017 -- Current}
		{iOS Developer}
		{BBVA Bancomer}
		{BBVA Plan - BBVA Send - BBVA Multipagos - Somos BBVA
		\\ \texttt{MVVM - VIPER - Clean Architecture}\slashsep\texttt{Design Patterns (Observer, Delegate)}\slashsep\texttt{CoreData - Realm}\slashsep		
		 \texttt{Keychain}\slashsep\texttt{Autolayouts}\slashsep\texttt{Scrum Agile}		
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2010 -- 2016}
		{Licenciatura en Ingenier\'ia en Ciencias Computacionales}
		{Benem\'erita Universidad Aut\'onoma de Puebla}
		%{\lorem}
		{

Ganador 3er. Concurso Estudiantil, Prototipos de Innovación
Tecnológica 2016 con aplicación para la prevención de feminicidios en
el estado de Puebla, “BUSSA”.

Escuela de Verano Computación 2015, DEPARTAMENTO APLICACIONES DE MICROCOMPUTADORAS. Investigación con Dr.Harold V. McIntosh (Pionero de la computación en México).

Escuela de Verano Computación 2014, DEPARTAMENTO APLICACIONES DE MICROCOMPUTADORAS. Investigación con Dr. Harold V. McIntosh (Pionero de la computación en México).

Fundador “Laboratorio Harold V. McIntosh” (iLab BUAP FCC).
Mantenimiento Preventivo y Correctivo a equipo Apple, y desarrollo de
aplicaciones móviles. 2013-2016.

Escuela de Verano Computación 2013, DEPARTAMENTO APLICACIONES DE MICROCOMPUTADORAS. Investigación con Dr. Harold V. McIntosh (Pionero de la computación en México).		
		
Integrante Comunidad "Sistema Operativo Aztli Gnu/Linux" 2010-2013.
		}
		
	%\entry
		%{2014}
		%{Postgraduate Diploma}
		%{A University Name}
		%{\lorem\lorem}
	%\entry
		%{2007 -- 2013}
		%{Bachelor's Degree}
		%{A University Name}
		%{\lorem\lorem}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Spanish} - native\\
	\textbf{English} - proficient\\
	%\textbf{Polish} - rudimentary
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	%I love... \lorem
	I like watch movies and if i have time i love read universal literature.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	%I help... \lorem
	I help other people learn to code in a basic way.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
